### 2021-02-09 SupplementaryMaterial/Abstract.tex
update

\vspace{-0.3in}
Side-channel

>>>>

\vspace{-0.3in}
Side-channel attacks can leak secret information unconsciously from non-functional characteristics, e.g., time, power, and memory usage. Similar to many other vulnerabilities in software, attackers exploit the flaws in designs of hardware and implementations of software. Contrary to the the hardware countermeasures, which usually need changes to the complex underlying hardware, software solutions are more easier to adopt in many scenarios. This dissertation study various aspects of the side-channel vulnerabilities.

The first step is to identify side-channel leakages.
